Surface correlation functions calculations: improving methodology for discrete images with novel exact continuous approach

### 2023-03-23 paper.tex
A little clarification regarding isotropic media

Now we define two disjoint sets in a homogeneous porous medium: a set of solid
phase $S$ and a set of void phase $V$. Surface-surface correlation function
$F_{ss}$ and surface-void correlation function $F_{sv}$ are then defined as follows:
\begin{align}
  F_{ss}(\bm{r}) &= \langle |\nabla \chi_S(\bm{x})| |\nabla \chi_S(\bm{x} +
  \bm{r})| \rangle \label{eq:fss} \\
  F_{sv}(\bm{r}) &= \langle |\nabla \chi_S(\bm{x})| \chi_V(\bm{x} +
  \bm{r}) \rangle \label{eq:fsv}
\end{align}
Here the brackets $\langle \dots \rangle$ denote ensemble average. For isotropic
homogeneous media vector values $\bm{x}$ and $\bm{r}$ can be replaced with
scalars. In case correlation functions are computed in predefined directions,
scalar values can be also used for anisotropic structures
\cite{jiao2014chawla,EPL1}.

@@

\section{Conclusion}
In this paper we develop an algorithm for precise calculation of surface-surface
correlation function for two-dimensional sets with smooth boundary and checked
our fast algorithm using these new cases. The fast algorithm was improved using
a wider filter $H'$.

>>>>

Now we define two disjoint sets in a homogeneous porous medium: a set of solid
phase $S$ and a set of void phase $V$. Surface-surface correlation function
$F_{ss}$ and surface-void correlation function $F_{sv}$ are then defined as follows:
\begin{align}
  F_{ss}(\bm{r}) &= \langle |\nabla \chi_S(\bm{x})| |\nabla \chi_S(\bm{x} +
  \bm{r})| \rangle \label{eq:fss} \\
  F_{sv}(\bm{r}) &= \langle |\nabla \chi_S(\bm{x})| \chi_V(\bm{x} +
  \bm{r}) \rangle \label{eq:fsv}
\end{align}
Here the brackets $\langle \dots \rangle$ denote ensemble average. If the medium
under consideration is also isotropic, the argument in functions $F_{ss}$ and
$F_{sv}$ can be replaced with a scalar:
\begin{align*}
  F_{ss}(r) &= F_{ss}(|\bm{r}|) \\
  F_{sv}(r) &= F_{sv}(|\bm{r}|)
\end{align*}
In case correlation functions are computed in predefined directions, scalar
values can be also used for anisotropic structures \cite{jiao2014chawla,EPL1}.

@@

\section{Conclusion}
% Is this a right label?
\label{sec:summary}
In this paper we develop an algorithm for precise calculation of surface-surface
correlation function for two-dimensional sets with smooth boundary and checked
our fast algorithm using these new cases. The fast algorithm was improved using
a wider filter $H'$.
